Classless Java: Tuning Java Interfaces

### 2015-12-02 paper/sections/Implementation.tex
Game example
small stuff

\section{Implementation with Lombok}

Our implementation is based on extension to Lombok. The Lombok
project~\cite{lombok} is a Java tool that aims at removing (or
reducing) Java boilerplate code as far as possible, via
annotations. There are a number of annotations provided by the
original Lombok, including \textbf{@Getter}, \textbf{@Setter},
\textbf{@ToString} for generating getters, setters and \QM{toString}
methods, respectively.  Furthermore, Lombok provides a number of
interfaces for users to create custom transformations, as extensions
to the original framework.
A transformation is based on a handler, which acts on the AST from
parsing the annotated node and returns a modified AST for analysis and
generation afterwards. Such a handler can either be a Javac handler or
an Eclipse handler.

>>>>

\section{Implementation}

Our implementation is based on an extension to Lombok. The Lombok
project~\cite{lombok} is a Java tool that aims at removing (or
reducing) Java boilerplate code via
annotations. There are a number of annotations provided by the
original Lombok, including \textbf{@Getter}, \textbf{@Setter},
\textbf{@ToString} for generating getters, setters and \QM{toString}
methods, respectively.  Furthermore, Lombok provides a number of
interfaces for users to create custom transformations, as extensions
to the original framework.
A transformation is based on a handler, which acts on the AST from
parsing the annotated node and returns a modified AST for analysis and
generation afterwards. Such a handler can either be a Javac handler or
an Eclipse handler.

### 2015-12-02 paper/sections/RelatedWork.tex

There are also proposals for extending Java (before Java8) with
traits. For example, FeatherTrait Java (FTJ)~\cite{Liquori08ftj} by
Liquori et al. extends the calculus of Featherweight Java
(FJ)~\cite{Igarashi01FJ} with statically-typed traits, adding
trait-based inheritance in Java.  Except for few, mostly syntactic
details, their work can be emulated/rephrased with Java8 interfaces.
There are also extensions to the original trait model, which have operations 
that default methods and interfaces cannot model, such as method renaming
(as in [Reppy2006]), which breaks structural subtyping.

\paragraph{Traits vs Object Interfaces}
We consider object interfaces to be an alternative to traits or mixins.  In the
trait model two concepts (traits and classes) coexist and cooperate. Some
authors~\cite{bettini2013pure} see this as good language design fostering good
software development by helping programmers to think about the structure of
their programs.  However, other authors see the need of two concepts and the
absence of state as drawbacks of this model~\cite{malayeri2009cz}.  Object
interfaces are units of reuse, and at the same time they provide factory methods
for instantiation and support state.  Our approach promotes the use of
interfaces instead of classes, in order to rely on the modular composition
offered by interfaces. Since Java was designed for classes, a direct class-less
programming style is verbose and feels unnatural. However, annotation driven
code generation is enough to overcome this difficulty, and the resulting
programming style encourages modularity, composability and reusability, by
keeping a strong object oriented feel. In that sense, we promote object
interfaces as being both units of reusable code and object factories. Our
practical experience is that, in Java, separating the two notions leads to alot
of boilerplate code, and is quite limiting when multiple inheritance with state
is required. The use of abstract state operations avoids the key difficulties
associated with multiple inheritance and state, while still being quite
expressive.  Moreover the ability to support constructors adds additional
expressivity, which is not available in approaches such as Scala's
traits/mixins.

>>>>

There are also proposals for extending Java (before Java8) with traits. For
example, FeatherTrait Java (FTJ)~\cite{Liquori08ftj} by Liquori et al. extends
the calculus of Featherweight Java (FJ)~\cite{Igarashi01FJ} with
statically-typed traits, adding trait-based inheritance in Java.  Except for
few, mostly syntactic details, their work can be emulated/rephrased with Java8
interfaces.  There are also extensions to the original trait model, which have
operations that default methods and interfaces cannot model, such as method
renaming in \cite{reppy2006foundation}, which breaks structural subtyping.

\paragraph{Traits vs Object Interfaces}
We consider object interfaces to be an alternative to traits or mixins.  In the
trait model two concepts (traits and classes) coexist and cooperate. Some
authors~\cite{BettiniDSS13} see this as good language design fostering good
software development by helping programmers to think about the structure of
their programs.  However, other authors see the need of two concepts and the
absence of state as drawbacks of this model~\cite{malayeri2009cz}.  Object
interfaces are units of reuse, and at the same time they provide factory methods
for instantiation and support state.  Our approach promotes the use of
interfaces instead of classes, in order to rely on the modular composition
offered by interfaces. Since Java was designed for classes, a direct class-less
programming style is verbose and feels unnatural. However, annotation driven
code generation is enough to overcome this difficulty, and the resulting
programming style encourages modularity, composability and reusability, by
keeping a strong object oriented feel. In that sense, we promote object
interfaces as being both units of reusable code and object factories. Our
practical experience is that, in Java, separating the two notions leads to alot
of boilerplate code, and is quite limiting when multiple inheritance with state
is required. The use of abstract state operations avoids the key difficulties
associated with multiple inheritance and state, while still being quite
expressive.  Moreover the ability to support constructors adds additional
expressivity, which is not available in approaches such as Scala's
traits/mixins.

### 2015-12-02 paper/sections/Translation.tex

@@

\hl{To translate an interface annotated by \mixin, we add some other methods for type refinement, then add a new annotation \textbf{@ObjWeak} to the interface.}

@@

\hl{To translate an interface annotated by \textbf{@ObjWeak}, we add the $\QM{of}$ method.}
However, first of all we check if the interface is valid for annotation:

>>>>

Two translation functions for the two parts are presented as follows:

@@

\noindent\hl{To translate an interface annotated by \mixin, we add some other methods for type refinement, then add a new annotation \textbf{@ObjWeak} to the interface.}

@@

\noindent\hl{To translate an interface annotated by \textbf{@ObjWeak}, we add the $\QM{of}$ method.}
However, first of all we check if the interface is valid for annotation:
